Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ The Online Survey

### 2017-09-14 cloverflow_technical_report/cloverflow_survey_rn.tex
Latest update of the RN.

\title{Awareness of Stack Overflow Users to\\ Outdated and License-violating Code:\\ The Online Survey}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

%This study is interested in the problem of outdated code and software licensing
%violations caused by code cloning on Internet-based question and answer
%websites. 
Recent research shows that outdated third-party code and software
licensing conflicts are ramifications by reusing source code by copying and
pasting (i.e.~code cloning). \cite{Xia2014} report that a large number of open
source systems reuse outdated third-party libraries from popular open source
projects. Using the outdated code give detrimental effects to the software since
they may introduce vulnerabilities. On the other hand, \cite{German2009} found
that code cloning leads to conflicts in software license among different
systems.

The Internet encourages fast and easy code cloning by sharing and copying code
to and from online sources. Developers nowadays do not only clone code from local
software projects, but also from online sources such as programming Q\&A website
and online code repositories~\FIXME{Add citation}. Stack Overflow is one of the most popular
programming Q\&A websites in the word. It has 7.6 million users, 14 million
questions, 23 million answers\footnote{Data as of 21 August 2017
	from~\url{https://stackexchange.com/sites}}, and more than 50 million developers
visiting each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}. Nevertheless, several code snippets on Stack
Overflow are found to be problematic. Many code snippets provided as solutions
are workarounds and occasionally contains defects or vulnerabilities.
\cite{Acar2016} performed a user study and found that Stack Overflow helps
developers to solve Android programming problems quicker than other resources
while, at the same time, offers less secure code than books or the official
Android documentation. Only 17\% of the Stack Overflow discussion threads the
participant visited during the study contain secure code snippets. They also
found that similar piece of API call copied from Stack Overflow by participants
in their study existed in a random sample of 200,000 Android apps from Google
Play. \cite{An2017} showed that 1,279 cloned snippets between 399 Android apps
and Stack Overflow potentially violate software licenses.

\textbf{We are interested in studying the issues of outdated code and software license
violation cause by code snippets on Stack Overflow.} Asking and answering
questions on Stack Overflow usually involve copying and pasting source code
snippets, either in a question or an answer. However, the copied snippets are
not regularly checked and occasionally not up-to-date with their originals. Some
snippets are copied from an open source system with stricter software license
than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior to
this study, we performed an empirical study using code clone detection tools
to locate cloned code snippets in accepted answers. We found that many snippets
were copied from open source projects. Some cloned snippets are outdated and
possibly violating the original software license. In either case, these snippets
are potentially harmful for reuse. To accompany the findings and gain
insights into the cause of the problems, we resort to a qualitative study using
an online survey of Stack Overflow developers who 1) answer programming
questions with code snippets and 2) reuse code snippets from Stack Overflow
answers.

In this paper, we use the term ``answerers'' to refer to Stack Overflow users
who have high reputation, specifically the users with reputation from 963,731
(highest)  to 6,999. The answerers gain their reputation from answering
questions and receiving votes from other users. The reputation reflects trust
they gain from other users and their activeness in answering questions. We ask
the answerers the origins of source code snippets in their answers  and assess
their awareness of outdated and licensed code. 
We use the term ``visitors'' the
refer to developers, who may or may not have a Stack Overflow account but visit
Stack Overflow when facing programming problems. They copy example code snippets
that are relevant to their problems and reused them in their software. 
We ask Stack Overflow visitors, who copied code snippets from
Stack Overflow, about their experience of outdated or license-violating code.

\section{Research Questions}
In this study, we would like to answer seven research questions listed below. The first three questions will be
answered by the Stack Overflow answerer survey, while the last three questions will be answered by the
Stack Overflow visitor survey.

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ4 (Importance of Stack Overflow to developers):} \textit{Why developers choose to find programming solutions on Stack Overflow?}
	\item \textbf{RQ5 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
	\item \textbf{RQ6 (Awareness of Stack Overflow visitors to CC BY-SA 3.0 license):} \textit{Are Stack Overflow visitors aware of the the CC BY-SA 3.0 license enforced by Stack Overflow?}
	\item \textbf{RQ7 (Software licensing issues from Stack Overflow code snippets):} \textit{How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
\end{enumerate}

\section{Research Methodology}
The study is performed using an online survey. We designed the survey using
Google Forms by following the principles of survey research
by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. 
We created two versions of the
survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. 
The surveys are completely anonymous and the participants could decide to leave at
any time. It does not collect any sensitive personal information from the
participants and were approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at UCL.  The complete version of
the surveys can be found in the Appendix~\ref{appendixA}.

\subsection{The Answerer Survey}
The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions were mandatory while the other 9 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, experience of
answering Stack Overflow questions, sources of the Stack Overflow snippets,
concerns of copying code snippets to Stack Overflow, problems from code 
snippets on Stack Overflow, fixing outdated code, and additional feedbacks.

@@

We selected the participants for our answerer survey based on their Stack Overflow reputation. On
Stack Overflow, a user's reputation reflects how much the community trust the
user. A user earns reputation when he or she receives up votes for good
questions and useful answers. Accepted answers receive more reputation score
than questions, and regular answers\footnote{Stack Overflow
	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

The participants were invited to take the survey via email addresses publicly available on their
public Stack Overflow and GitHub profiles. We selected the answerers based on
all-time reputation ranking\footnote{Stack Overflow Users (data as of 25 July
	2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}} and
separated them into two groups (see Table~\ref{tab:answerers}) so that we can
compare the results or observe similar patterns between them. 
The first group had reputation from 963,731 (the
highest) to 7,674, and the second group had reputation from 7,636 to 6,999 which
we sent out 300 and 307 emails (excluding undelivered ones) respectively. The
survey was open for participation for a month, from 25 July 2017 to 25 August
2017, before we collected and analysed the responses.

@@

The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
questions. The first four questions were mandatory while the other 12 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, importance of
Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
Stack Overflow snippets, licensing of code on Stack Overflow, and additional
feedbacks.

@@

The participants for this survey were invited to take the survey via five
channels. The first channel is via the first author's Facebook post where the
first author invited friends who are software developers and have experience of
copying code snippets from Stack Overflow to take the survey. The second channel
is a popular Thai technology news and media community called blognone.com which
attracts a high number of software developers. The first author posted an
invitation to the visitor survey in a discussion forum. The third channel
collects answers from University of Molise which is the third author's
workplace. The last two channels are from a comp.lang.java.programmer Google
groups and Software Engineering Facebook page. The survey was open for
participation for a month, from 25 July 2017 to 25 August 2017, before we
collected and analysed the responses. The number of participants taken the
survey are shown in Table~\ref{tab:visitors}.

@@

\subsection{Answerer Responses}
We received 117 answers (39\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups were high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

@@

The majority of users in both groups are experienced developers with more than
10 years of experience or between 5 to 10 years as depicted in
Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 that
have more than 10 year of software development experience, while a slightly less
percentage of 50\% in Group 2.

The participants are active users and regularly answer questions on Stack
Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty two (82\%) and
sixty (60\%) of answerers from Group 1 and Group 2  answer questions at
least once a week.
More than half of the answerers very frequently (81--100\% of the time) or
frequently (61--80\% of the time) include code snippets in their answers. To
break down into two groups as depicted in
Figure~\ref{fig:survey_answer_frequency_with_code}, Group 1 very frequently
(48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise,
Group 2 does the same (very frequently for 32.1\% and frequently for 36.9\%).

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2cm]{0.98\textwidth}{%
		\textit{For RQ 1, we found that answering questions by writing the new code from
			scratch is the most popular choice for Stack Overflow answerers followed by modifying from the code in question, or copying from personal projects. Other less
			popular choices include copying code from open
			source projects and from other sources. Copying code from company projects are the least popular choice.} }%
}
\vspace{0.5cm}

@@

Almost every answerer in both groups (98\% and 99\% respectively) does not
include license statement in their code snippets (numbers are shown in
Figure~\ref{fig:survey_license}). Some of the participants explain the reason in
the open comment question which we summarised into three groups as follows.
First, they choose to post only their own code or code that is adapted from the
question. The code is automatically subjected to Stack Overflow's CC BY-SA 3.0.
Second, they copy code from company or open source projects that they know are
permitted to be publicly distributed. Hence, no license statement is required.
Third, some answerers believe that code snippets in their answers are too small
to claim any intellectual property on them and fall under fair
use~\citep{fairuse}.

@@

We then shift the focus to only Stack Overflow. We ask the participants how frequently they reuse code snippets from answers on Stack Overflow.
According to the answers (see Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we found that 57 (64\%) participants actively reusing
code snippets from Stack Overflow. Eight participants (9\%) copy Stack Overflow
code everyday, 22 (25\%) do copying 3-6 times a week, 27 (30\%) do copying once or twice a week. There are 2 participants (2\%) who never
copy code from Stack Overflow.

@@

To understand why the participants choose to copy code snippets from Stack
Overflow, we asked them to rate four reasons in Likert's scale (Strongly agree,
Agree, Undecided, Disagree, Strongly disagree). The four reasons include
\textit{They are easy to find by searching the web}, \textit{They solve problems
	similar to my problems with minimal changes}, \textit{The context of questions
	and answers helped me understand the code snippets better}, \textit{The voting
	mechanism and accepted answers helped filtering good code from bad code}. The
answers are depicted in Figure~\ref{fig:survey_visitor_why_copy_so}. More than 80\% of the
participants agree with all the four reasons.

@@

Stack Overflow is a gold mine for software engineering research and has been put
to use in several previous studies. In terms of developer-assisting tools,
Seahawk is an Eclipse plug-in that searches and recommends relevant code
snippets from Stack Overflow~\citep{Ponzanelli2013}. A follow up work, Prompter,
by Ponzanelli et al.~\citep{Ponzanelli2014} achieves the same goal but with
improved algorithms. The code snippets on Stack Overflow are mostly examples or
solutions to programming problems. Hence, several code search systems use whole
or partial data from Stack Overflow as their code search
databases~\citep{Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015}. Furthermore, Treude et
al.~\cite{Treude2016}~use machine learning techniques to extract insight
sentences from Stack Overflow and use them to improve API documentation.

@@

\subsection{Software Licensing}
Software licensing is crucial for open source and industrial software
development. Di Penta et al.~\cite{DiPenta2010} studied the evolution of
software licensing in open source software and found that licensing statements
change over time. \cite{German2009} found that licensing conflicts occur between
the clone siblings, i.e.~clones among different systems that come from the same
source. Later, \cite{German2010} created an automated tool for software license
identification, Ninka. \cite{An2017} detected clones between 399 Android apps
and Stack Overflow Java code snippets. They found that  that 1,279 cloned
snippets potentially violate software licenses. Our study gives insights into
the software licensing of Stack Overflow code snippets. We study the licensing
awareness of developers when they copy and paste code to/from Stack Overflow.

\subsection{Reusing of outdated third-party source code} 
Outdated code occurs in software development. Xia et al.~\cite{Xia2014} discover
that there are code reused from popular open source projects in a large number
of open source systems. More importantly, some of the reused code are outdated
which affect quality and security of the software. Our study focuses on a
similar problem but on the context of Stack Overflow.

@@

From the answerer's responses, we discovered that code in Stack Overflow answers are usually written from
scratch to answer a question. Nonetheless, there are some code snippets that are
copied from the answerers' personal, open source, or company projects.

Outdated code on Stack Overflow occurs when the code snippet in an answer is
copied from another location and is no longer up-to-date. The results show that
although the answerers are aware of outdated code in their answers, 19\% of them
rarely or never fix the code.

Regarding the software license, approximately 60\% of the answerers are aware
of Stack Overflow CC BY-SA 3.0. Ninety-eight to ninety-nine percent do not include
license in their answers nor check for licensing conflicts when they copy code from
another location and paste in the answer.

>>>>

\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ The Online Survey}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

%This study is interested in the problem of outdated code and software licensing
%violations caused by code cloning on Internet-based question and answer
%websites.
Recent research shows that outdated third-party code and software licensing
conflicts are ramifications by code cloning, i.e.~reusing source code by copying
and pasting. \cite{Xia2014} report that a large number of open source systems
reuse outdated third-party libraries from popular open source projects. Using
the outdated code give detrimental effects to the software since they may
introduce vulnerabilities. On the other hand, \cite{German2009} found that code
cloning leads to conflicts in software license among different systems.

The Internet encourages fast and easy code cloning by sharing and copying the
code to and from online sources. Developers nowadays do not only clone code from
local software projects, but also from online sources such as programming Q\&A
website and online code
repositories~\citep{Acar2016,Abdalkareem2017,An2017,Yang2017}. Stack Overflow is
one of the most popular programming Q\&A websites in the world. It has 7.6
million users, 14 million questions, 23 million answers\footnote{Data as of 21
	August 2017 from~\url{https://stackexchange.com/sites}}, and more than 50
million developers visiting each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}. Some code snippets on Stack Overflow are found
to be problematic. \cite{Acar2016} discovered that many code snippets provided
as solutions on Stack Overflow are workarounds and occasionally contains defects
or vulnerabilities. They performed a user study and found that although Stack
Overflow helps developers to solve Android programming problems quicker than
other resources, at the same time, offers less secure code than books or the
official Android documentation. Only 17\% of the Stack Overflow discussion
threads the participant visited during the study contain secure code snippets.
They also found a similar piece of an API call copied from Stack Overflow by
participants in their study occurring in a random sample of 200,000 Android apps
from Google Play. In addition, \cite{An2017} investigated clones between 399
Android apps and Stack Overflow posts. They found 1,226 code snippets which were
reused from 68 Android apps. They also observed that there are 1,279 cases of
potential license violations.

Asking and answering questions on Stack Overflow involves including source code
snippets, either in a question or an answer or both. While many answers contain
snippets that are written from scratch, there are several answers containing
code snippets copied from other sources. The copied snippets on Stack Overflow
is a snapshot of the code at the time of copying. They are less frequently
updated than in normal software projects and might not be up-to-date with their
originals, which are further modified due to bug fixing or feature improvements.
In addition, Some snippets are copied from software systems with stricter
license than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA
3.0). Prior to this study, we performed a quantitative empirical study using
code clone detection tools to locate cloned code snippets in accepted answers.
We found that many snippets were copied from open source projects. Some cloned
snippets are outdated (or obsolete) and some possibly violate the original software license.
These snippets are potentially harmful to reuse. To accompany the findings and
gain insights into the cause of the problems, we resort to a qualitative study
using an online survey of Stack Overflow developers who 1) regularly answer
programming questions with code snippets and 2) reuse code snippets from Stack
Overflow. \textbf{The study aims to understand the developers' awareness and
	experience to the issues of outdated and license-violating code on Stack
	Overflow.}

In this paper, we use the term ``answerers'' to refer to Stack Overflow users
who actively answer questions, which is measured by their reputation. The
answerers gain a reputation from giving a helpful answer to a question and
receiving votes from other users. The reputation reflects trust they gain from
other users and also the quality of their answers. We ask the answerers the
origins of source code snippets in their answers, assess their awareness of
outdated and licensed code, and understand how they handle the issues.

We use the term ``visitors'' the refer to developers, who may or may not have a
Stack Overflow account but visit Stack Overflow when they encounter programming
problems. They copy code snippet(s) in a solution that is relevant to their
problem and reused them with or without a modification. We ask the visitors
about their experience of reusing source code from Stack Overflow and the problems
they faced including code obsolescence and software license.

\section{Research Questions}
In this study, we would like to answer six research questions. The first three questions will be
answered by the Stack Overflow answerer survey, while the other three questions will be answered by the
Stack Overflow visitor survey.

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
	\item \textbf{RQ5 (Software licensing issues from Stack Overflow code snippets):}\textit{How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
\end{enumerate}

\section{Research Methodology}
The study is conducted using online surveys. We designed the surveys using
Google Forms by following the principles of survey research
by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. We created two versions of the
survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. Both
surveys are completely anonymous and the participants could decide to leave at
any time. They do not collect any sensitive personal information from the
participants and are approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at University College London (UCL). 
The complete version of the surveys can be found in 
Appendix~\ref{appendixA}.

\subsection{The Answerer Survey}
The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions are mandatory while the other 9 questions will
be shown to the participants based on their previous answers. The survey
collects information of the participant's software development experience, the
experience of answering Stack Overflow questions, sources of the Stack Overflow
snippets, awareness of outdated code in their answers, concerns regarding
license when they copy code snippets to Stack Overflow, and additional feedbacks.

@@

We selected the participants for our answerer survey based on their Stack
Overflow reputations. On Stack Overflow, a user's reputation reflects how much
the community trusts the user. A user earns reputation when he or she receives
up votes for good questions and useful answers. Accepted answers receive more
reputation score than questions and regular answers\footnote{Stack Overflow
	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

The participants were invited to take the survey via email addresses publicly
available on their Stack Overflow and GitHub profiles. We selected the answerers
based on their all-time reputation ranking\footnote{Stack Overflow Users (data as of
	25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}
and separated them into two groups (see Table~\ref{tab:answerers}) so that we
can compare the results or observe similar patterns between them. The first
group had reputation from 963,731 (the highest) to 7,674, and the second group
had reputation from 7,636 to 6,999 which we sent out 300 and 307 emails
(excluding undelivered ones) respectively. The survey was open for participation
for a month, from 25 July 2017 to 25 August 2017, before we collected and
analysed the responses.ponses.

@@

The Stack Overflow visitor survey consists of 16 questions: 9 Likert's scale
questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
questions. The first four questions were mandatory while the other 12 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, the importance of
Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
Stack Overflow snippets, licensing of code on Stack Overflow, and additional
feedbacks.

@@

The participants for this survey were invited to take the survey via five
channels. The first channel is via the first author's Facebook post where the
first author invited friends who are software developers and have experience of
copying code snippets from Stack Overflow to take the survey. The second channel
is a popular Thai technology news and media community called blognone.com which
attracts a high number of software developers. The first author posted an
invitation to the visitor survey in a discussion forum. The third channel
collects answers from the University of Molise which is the third author's
workplace. The last two channels are from a comp.lang.java.programmer Google
groups and Software Engineering Facebook page. The survey was open for
participation for a month, from 25 July 2017 to 25 August 2017, before we
collected and analysed the responses. The number of participants taken the
survey is shown in Table~\ref{tab:visitors}.

@@

\subsection{Answerer Responses}
We received 117 answers (39\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups was high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

@@

The majority of users in both groups are experienced developers with more than
10 years of experience or between 5 to 10 years as depicted in
Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 that
have more than 10 years of software development experience, while a slightly less
percentage of 50\% in Group 2.

The participants are active users and regularly answer questions on Stack
Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty-two (82\%) and
sixty (60\%) of answerers from Group 1 and Group 2  answer questions at
least once a week.
More than half of the answerers very frequently (81--100\% of the time) or
frequently (61--80\% of the time) include code snippets in their answers. To
break down into two groups as depicted in
Figure~\ref{fig:survey_answer_frequency_with_code}, Group 1 very frequently
(48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise,
Group 2 does the same (very frequently for 32.1\% and frequently for 36.9\%).

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2cm]{0.98\textwidth}{%
        \textit{For RQ 1, we found that answering questions by writing the new
	code from scratch is the most popular choice for Stack Overflow
	answerers followed by modifying the code in question or copying from
	personal projects. Other less popular choices include copying code from
	open source projects and from other sources. Copying code from company
	projects are the least popular choice.} }%
}
\vspace{0.5cm}

@@

Almost every answerer in both groups (98\% and 99\% respectively) does not
include license statement in their code snippets (numbers are shown in
Figure~\ref{fig:survey_license}). Some of the participants explain the reason in
the open comment question which we summarised into three groups as follows.
First, they choose to post only their own code or code that is adapted from the
question. The code is automatically subjected to Stack Overflow's CC BY-SA 3.0.
Second, they copy the code from company or open source projects that they know are
permitted to be publicly distributed. Hence, no license statement is required.
Third, some answerers believe that code snippets in their answers are too small
to claim any intellectual property on them and fall under fair
use~\citep{fairuse}.

@@

We then shift the focus to only Stack Overflow. We ask the participants how
frequently they reuse code snippets from answers on Stack Overflow. According to
the answers (see Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we
found that 57 (64\%) participants actively reusing code snippets from Stack
Overflow. Eight participants (9\%) copy Stack Overflow code every day, 22 (25\%)
do copying 3-6 times a week, 27 (30\%) do copying once or twice a week. There
are 2 participants (2\%) who never copy the code from Stack Overflow.

@@

To understand why the participants choose to copy code snippets from Stack
Overflow, we asked them to rate four reasons in Likert's scale (Strongly agree,
Agree, Undecided, Disagree, Strongly disagree). The four reasons include
\textit{They are easy to find by searching the web}, \textit{They solve problems
	similar to my problems with minimal changes}, \textit{The context of questions
	and answers helped me understand the code snippets better}, \textit{The voting
	mechanism and accepted answers helped to filter good code from bad code}. The
answers are depicted in Figure~\ref{fig:survey_visitor_why_copy_so}. More than 80\% of the
participants agree with all the four reasons.

@@

Stack Overflow is a gold mine for software engineering research and has been put
to use in several previous studies. In terms of developer-assisting tools,
Seahawk is an Eclipse plug-in that searches and recommends relevant code
snippets from Stack Overflow~\citep{Ponzanelli2013}. A follow-up work, Prompter,
by Ponzanelli et al.~\citep{Ponzanelli2014} achieves the same goal but with
improved algorithms. The code snippets on Stack Overflow are mostly examples or
solutions to programming problems. Hence, several code search systems use whole
or partial data from Stack Overflow as their code search
databases~\citep{Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015}. Furthermore, Treude et
al.~\cite{Treude2016}~use machine learning techniques to extract insight
sentences from Stack Overflow and use them to improve API documentation.

@@

\subsection{Software Licensing} Software licensing is crucial for open source
and industrial software development. Di Penta et al.~\cite{DiPenta2010} studied
the evolution of software licensing in open source software and found that
licensing statements change over time. \cite{German2009} found that licensing
conflicts occur between the clone siblings, i.e.~clones among different systems
that come from the same source. Later, \cite{German2010} created an automated
tool for software license identification, Ninka. \cite{An2017} detected clones
between 399 Android apps and Stack Overflow Java code snippets. They found  that
1,279 cloned snippets potentially violate software licenses. Our study gives
insights into the software licensing of Stack Overflow code snippets. We study
the licensing awareness of developers when they copy and paste code to/from
Stack Overflow.

\subsection{Reusing of outdated third-party source code} Outdated code occurs in
software development. Xia et al.~\cite{Xia2014} discover that there is code
reused from popular open source projects in a large number of open source
systems. More importantly, some of the reused code is outdated which affect
quality and security of the software. Our study focuses on a similar problem but
on the context of Stack Overflow.

@@

From the answerer's responses, we discovered that code in Stack Overflow answers
is usually written from scratch to answer a question. Nonetheless, there are
some code snippets that are copied from the answerers' personal, open source, or
company projects.

The outdated code on Stack Overflow occurs when the code snippet in an answer is
copied from another location and is no longer up-to-date. The results show that
although the answerers are aware of outdated code in their answers, 19\% of them
rarely or never fix the code.

Regarding the software license, approximately 60\% of the answerers are aware of
Stack Overflow CC BY-SA 3.0. Ninety-eight to ninety-nine percent do not include
the license in their answers nor check for licensing conflicts when they copy
the code from another location and paste in the answer.
